### 2024-01-06 tesis_Ashish/Chapter4/chapter4.tex
Updated thesis 5 Jan 2024
Updated thesis 6 Jan 2024

@@

Instantaneous luminosity refers to the rate of collisions at any given moment in time. It is a snapshot of the experiment's performance and is represented as \( L_{\text{inst}} \). The unit of instantaneous luminosity is often Hertz per micro barn $(Hz/ub)$. Integrated luminosity is the accumulation of instantaneous luminosity over a specific time period. Mathematically, it is defined as:
\[
\text{Integrated Luminosity} = \int (\text{Instantaneous Luminosity}) \, dt
\]
The unit of integrated luminosity is typically inverse femtobarns (\( \text{fb}^{-1} \)). Integrated luminosity can be understood as the sum of all instantaneous luminosities over the duration of the experiment, enhancing the statistical significance of the data collected. It serves as a measure of the total number of events recorded by the experiment, crucial for robust statistical analysis. When plotted as a function of lumi sections, PCC instantaneous and integrated luminosity offer distinct yet complementary insights into the experiment's performance. In plots that feature luminosity as a function of these lumi sections, the x-axis enumerates the lumi sections while the y-axis presents the luminosity values.  For instantaneous luminosity, discrete data points are plotted for each lumi section, providing immediate, lumi section specific measurements of the collision rate as shown in Fig. \ref{fig:PCC_inst_2018}. These points can fluctuate based on a variety of factors, such as beam conditions or adjustments to the accelerator. On the other hand, integrated luminosity is represented by a continuously ascending curve. Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section. The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.

>>>>

The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{pas_18} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV. Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events rate is 27.7 kHz. Trigger is applied on five colliding bunches due to limitation of the recording bandwidth.

@@

Instantaneous luminosity refers to the rate of collisions at any given moment in time. It is a snapshot of the experiment's performance and is represented as \( L_{\text{inst}} \). The unit of instantaneous luminosity is often Hertz per micro barn $(Hz/ub)$. Integrated luminosity is the accumulation of instantaneous luminosity over a specific time period. Mathematically, it is defined as:
\[
\text{Integrated Luminosity} = \int (\text{Instantaneous Luminosity}) \, dt
\]
The unit of integrated luminosity is typically inverse femtobarns (\( \text{fb}^{-1} \)). Integrated luminosity can be understood as the sum of all instantaneous luminosities over the duration of the experiment, enhancing the statistical significance of the data collected. It serves as a measure of the total number of events recorded by the experiment, crucial for robust statistical analysis. When plotted as a function of lumi sections, PCC instantaneous and integrated luminosity offer distinct yet complementary insights into the experiment's performance. In plots that feature luminosity as a function of these lumi sections, the x-axis enumerates the lumi sections while the y-axis presents the luminosity values.  For instantaneous luminosity, discrete data points are plotted for each lumi section, providing immediate, lumi section specific measurements of the collision rate as shown in Fig. \ref{fig:PCC_inst_2018}. These points can fluctuate based on a variety of factors, such as beam conditions or adjustments to the accelerator. On the other hand, integrated luminosity is represented by a continuously ascending curve. Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section. %The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.

### 2024-01-06 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 6 Jan 2024

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
\caption[Fill 8274 Luminosity Profile]{%                                                                                                                                                                                         
  PCC luminosity profile for Fill 8395.
}
\label{fig:period_bound_111}
\end{figure}

@@

PCC instantaneous luminosity provides a measure of the collider's performance and is graphically represented in Fig. \ref{fig:period_bound_1000045}. Each fill in the graph consistently displays a sequence of characteristics related to luminosity. The process initiates with ramp-up periods, where a swift increase in luminosity is evident. This surge is subsequently followed by leveling parts, where luminosity stabilizes and plateaus. As the fill progresses, burn-off parts emerge, marked by a gradual decline in luminosity. Interspersed within the graph are notable, sharp drops to lower luminosity levels, characteristic of emittance scans. As each fill reaches its culmination, pronounced drops are observable, signifying the end of fill events. This cyclical pattern is evident across all fills, underscoring the systematic nature of the process. Integrated luminosity accumulates this data over time. For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}. %\cite{bril2023randomzerobias}.

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
\caption[2022 PCC Inst. Luminosity]{%
  PCC instantaneous luminosity as a function of lumi section for entire 2022 year.

@@

\begin{table}[!htp]
  \centering
  \caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$ [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_label}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
\caption[Fill 8274 Luminosity Profile]{%                                                                                                                                                                                         
  PCC luminosity profile for Fill 8395.
}
\label{fig:period_bound_111}
\end{figure}

@@

PCC instantaneous luminosity provides a measure of the collider performance and is graphically represented in Fig. \ref{fig:period_bound_1000045}. Each fill in the graph consistently displays a sequence of characteristics related to luminosity. The process initiates with ramp-up periods, where a swift increase in luminosity is evident. This surge is subsequently followed by leveling parts, where luminosity stabilizes and plateaus. As the fill progresses, burn-off parts emerge, marked by a gradual decline in luminosity. Interspersed within the graph are notable, sharp drops to lower luminosity levels, characteristic of emittance scans. As each fill reaches its culmination, pronounced drops are observable, signifying the end of fill events. This cyclical pattern is evident across all fills, underscoring the systematic nature of the process. Integrated luminosity accumulates this data over time \cite{pas_22}. %For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}. %\cite{bril2023randomzerobias}.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
\caption[2022 PCC Inst. Luminosity]{%
  PCC instantaneous luminosity as a function of lumi section for entire 2022 year.

@@

\begin{table}[!htp]
  \centering
  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$ [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_label}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

### 2024-01-06 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 6 Jan 2024

\begin{table}[H]
  \centering
  \caption[dr offset values]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dphi cut values]{dphi cut values for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
    %-2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
    %-3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
    %-4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
    1  & 0.00088  & 0.0013   & 0.0015    & 0.0016   & 0.0017   \\
    2  & 0.00076   & 0.0011   & 0.0013   & 0.0014   & 0.0015   \\
    3  & 0.00068  & 0.00097  & 0.0012   & 0.0013   & 0.0013   \\
    4  & 0.00061  & 0.00088  & 0.0010   & 0.0011   & 0.0012   \\
  \end{tabular}
  \label{tab:mdphi_cuts_values}
\end{table}

@@

\newpage
\begin{table}[H]
  \centering
  \caption[dr mean values]{dr mean values (mm) obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\ 
%-3 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\ 
%-2 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\ 
%-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
1 & 0.023 & 0.031 & 0.039 & 0.047 \\
2 & 0.020 & 0.027 & 0.034 & 0.040 \\
3 & 0.018 & 0.023 & 0.029 & 0.035 \\
4 & 0.015 & 0.020  & 0.026 & 0.031 \\
\end{tabular}
\label{tab:my_label_55}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
1 & 0.0045 & 0.0045 & 0.0047 & 0.0052 \\
2 & 0.00442 & 0.0047 & 0.0048 & 0.0050 \\
3 & 0.0045 & 0.0045 & 0.0049 & 0.0049 \\
4 & 0.0045 & 0.0047 & 0.0049 & 0.0049 \\
\end{tabular}
\label{tab:my_label_53}
\end{table}

\begin{table}[H]
  \centering
  \caption[dphi cut values]{dphi standard deviation values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984 \\ 
%-3 & 0.000545699 & 0.000722289 & 0.00081899 & 0.000918094 \\ 
%-2 & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\ 
%-1 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
1 & 0.00063 & 0.00082 & 0.00094 & 0.0010 \\
2 & 0.00057 & 0.00076 & 0.00085 & 0.00090 \\
3 & 0.00052 & 0.00066 & 0.00077 & 0.00083 \\
4 & 0.00047 & 0.00059 & 0.00069 & 0.00075 \\
\end{tabular}
\label{tab:my_label_54}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{ashish_thesis/tepx_threefold_coincidences_1.png}
  \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}
  \label{fig:tepx_3foldcoin_allPU_1}
\end{figure}

>>>>

\begin{table}[H]
  \centering
  \caption[dr offset values for two-fold in phi]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values for two-fold in phi]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dphi cut values for two-fold in phi]{dphi cut values for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
    %-2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
    %-3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
    %-4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
    1  & 0.00088  & 0.0013   & 0.0015    & 0.0016   & 0.0017   \\
    2  & 0.00076   & 0.0011   & 0.0013   & 0.0014   & 0.0015   \\
    3  & 0.00068  & 0.00097  & 0.0012   & 0.0013   & 0.0013   \\
    4  & 0.00061  & 0.00088  & 0.0010   & 0.0011   & 0.0012   \\
  \end{tabular}
  \label{tab:mdphi_cuts_values}
\end{table}

@@

\newpage
\begin{table}[H]
  \centering
  \caption[dr mean values for two-fold in r]{dr mean values (mm) obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\ 
%-3 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\ 
%-2 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\ 
%-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
1 & 0.023 & 0.031 & 0.039 & 0.047 \\
2 & 0.020 & 0.027 & 0.034 & 0.040 \\
3 & 0.018 & 0.023 & 0.029 & 0.035 \\
4 & 0.015 & 0.020  & 0.026 & 0.031 \\
\end{tabular}
\label{tab:my_label_55}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values for two-fold in r]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
1 & 0.0045 & 0.0045 & 0.0047 & 0.0052 \\
2 & 0.00442 & 0.0047 & 0.0048 & 0.0050 \\
3 & 0.0045 & 0.0045 & 0.0049 & 0.0049 \\
4 & 0.0045 & 0.0047 & 0.0049 & 0.0049 \\
\end{tabular}
\label{tab:my_label_53}
\end{table}

\begin{table}[H]
  \centering
  \caption[dphi cut values for two-fold in r]{dphi standard deviation values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984 \\ 
%-3 & 0.000545699 & 0.000722289 & 0.00081899 & 0.000918094 \\ 
%-2 & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\ 
%-1 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
1 & 0.00063 & 0.00082 & 0.00094 & 0.0010 \\
2 & 0.00057 & 0.00076 & 0.00085 & 0.00090 \\
3 & 0.00052 & 0.00066 & 0.00077 & 0.00083 \\
4 & 0.00047 & 0.00059 & 0.00069 & 0.00075 \\
\end{tabular}
\label{tab:my_label_54}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{ashish_thesis/tepx_threefold_coincidences_1.png}
  \caption[Regions in XY plane showing three-fold coincidences]{Reconstructed three fold coincidences in all rings within TEPX double-disk.}
  \label{fig:tepx_3foldcoin_allPU_1}
\end{figure}
